The Driving Forces of API Evolution

### 2015-05-21 thesis/paper.tex
Updated last comment
improve->increse

%Gap in Literature
Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{dig2005role, hou2011exploring, shi2011empirical}. However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective.  %!!! still needs to be improved/increased (consider space re 1st page)

>>>>

%Gap in Literature
Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{dig2005role, hou2011exploring, shi2011empirical}. However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective. Our study will fill this gap by analysing an embedded platform API by using software evolution theories and by classifying the types of changes that occur. These types will be used in place of quantitative data which will make the results more tangible and will increase their usability.
